Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-05 paper/paper-nature_format.tex
more paper edits

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{March 30, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro and micro-level text analysis because it has only been
available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures all
proceedings of the Australian parliamentary debates from 1998 to the
present using Hansard. The database is publicly available and can be
linked to other datasets such as election results. The creation and
accessibility of this database enables the exploration of questions that
have not been possible to explore, serving as a valuable resource for
both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many Commonwealth countries such as Canada,
the United Kingdom, and Australia (Vice and Farrell 2017). Given the
content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, the Hansard has been digitized for 1901 to 2019 (Beelen et
al. 2017). Having a digitized version of Hansard enables researchers to
perform advanced analyses on these records using text analysis tools and
statistical modelling. Following the lead of that project, in this paper
we introduce a novel database for the Australian Hansard. This is
composed of individual datasets for each sitting day in the House of
Representatives from 1998 to 2022, containing details on everything said
in parliament in a form that can be readily used by researchers. With
the development of tools for large-scale text analysis, this database
will serve as a valuable resource for efficiently studying and exploring
political behaviour in Australia over time.

The Australian House of Representatives performs a number of crucial
governmental functions, such as creating new laws and overseeing
government expenditure (House of Representatives 2018, ch.~1). The House
operates under a parallel chamber setup, meaning there are two debate
venues where proceedings take place: the Chamber, and the Federation
Chamber. Sittings of the House follow a predefined order of business,
regulated by procedural rules called standing orders (House of
Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
number of scheduled proceedings including debates on government
business, 90 second member statements, and Question Time (House of
Representatives 2018, ch.~8). The Federation Chamber was created in 1994
as a subordinate debate venue of the Chamber. This allows for better
time management of House business as its proceedings occur
simultaneously with those of the Chamber (House of Representatives 2018,
ch.~21). Sittings in the Federation Chamber are quite different to those
of the Chamber in terms of their order of business and scope of
discussion. Business matters discussed in the Federation Chamber are
limited largely to intermediate stages of bill development, and the
business of private Members (House of Representatives 2018, ch.~21). It
is the recording and compilation of all of these proceedings on which
Hansard is based, and it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for
download from the official Parliament of Australia website in both PDF
and extensible markup language (XML) form. The PDF is the official
release. For early decades there is a need to digitize PDFs using
Optical Character Recognition (OCR) technology and there are many flaws
(Sherratt 2016). The PDF imposes formatting designed for humans to read
with ease, whereas XML is designed for consistency and machine
legibility. The nature of XML enables us to more easily use code to
manipulate these records at scale, motivating our choice to develop our
database solely using the XML formatted files. In cases where we were
unsure on how to proceed with processing the XML, we defer first to the
PDF, and then to the video recording of the proceeding, if available.

@@

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, Salisbury (2011) used online
Hansard records to investigate the occurrences of unparliamentary
comments by members of the House, where the Speaker tells that member to
withdraw their remark. Rasiah (2010) worked with Question Time data from
Hansard transcripts during February and March of 2003, to investigate
resistance of politicians in answering questions about Iraq. In their
work, Fraussen, Graham, and Halpin (2018) use Hansard to quantify
political prominence by investigating strategic mentions of interest
groups by elected officials. Finally, the work of Alexander and
Alexander (2021) offers a dataset of the Australian Hansard, along with
an analysis of the effect of elections and changes in Prime Ministers
upon topics mentioned in parliament. Alexander and Alexander (2021)
created this database with the static PDF versions of Hansard, using OCR
to digitize these files into text which is suitable for analysis. This
means there are considerable digitization errors especially in the first
half of the dataset.

While there is evidently a growing body of literature on this topic,
there is still no comprehensive database for Australian Hansard based on
XML that spans from 1901 to the present day. Our work serves to bridge
this gap.

@@

Our database contains one comma-separated value (CSV) file for each
sitting day of the House of Representatives from 02 March 1998 to 08
September 2022. We developed four scripts to produce all of these files,
where each script is designed to parse Hansard documents from a specific
portion of the 1998 to 2022 time frame.

This section will be structured as follows. First, we will provide an
overview of our approach to understanding and parsing an individual
Hansard XML document, which informed all four scripts used to create our
database. This will be supplemented with an excerpt from a Hansard XML
to provide a visual example of its structure. Next we will explain the
specific differences between the four scripts, and outline what
structural changes necessitated their separate development. We will then
provide details on the methodological intricacies of three core
components of Hansard proceedings: Question Time, interjections, and
stage directions. Finally, we will discuss the script we developed to
fill in remaining missing speaker details, which each file in our
database was passed to after being parsed and cleaned.

@@

The approach to parsing contents of an XML document is heavily dependent
on its tree structure. As such, to create this database, we started by
looking at a single Hansard XML transcript from 2019. Doing so enabled
us to identify the various components of interest in the document, and
how each one can be parsed according to its corresponding structural
form. Parsing was performed in \texttt{R} using the \texttt{XML} and
\texttt{xml2} packages (Temple Lang 2022; Wickham, Hester, and Ooms
2021). Focusing on one transcript also allowed us to ensure that all key
components of the transcript were being parsed and captured with as much
detail as possible. The typical form of a Hansard XML transcript is
summarized in the nested list below. Note that this provides a broad
overview of the structure, and does not contain every possible nested
element that may be found in a Hansard XML.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child-nodes,
where the first child-node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. Note that the Federation Chamber does not meet on
every sitting day, so this child element is not present in every XML
file. The use of separate child nodes allows for the distinction of
proceedings of the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with a business start which is
followed by a series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child-node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child-node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the speaker and the time of their first statement.
Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate
settings --- they are often composed of a series of interjections and
continuations. These statements are categorized under different
sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

Figure~\ref{fig-xml1} provides an example of the beginning of an XML
file for Hansard, which illustrates the structure outlined in the nested
list above. As stated, the XML structure begins with a parent element
\texttt{\textless{}hansard\textgreater{}} (highlighted in blue),
followed by a child element
\texttt{\textless{}session.header\textgreater{}} (highlighted in yellow)
with sub-child elements such as the date and parliament number, which
are all highlighted in pink. Next there is the child element containing
everything that takes place in the Chamber,
\texttt{\textless{}chamber.xscript\textgreater{}}, which is also
highlighted in yellow in Figure~\ref{fig-xml1}. As previously mentioned,
the first sub-node of \texttt{\textless{}chamber.xscript\textgreater{}}
is the business start. The structure of the business start can be seen
between the nodes highlighted in green in Figure~\ref{fig-xml1}, where
the content we parse from the business start is highlighted in orange.

@@

Evidently, the nature of XML formatting means that different pieces of
information are categorized under a series of uniquely named and nested
nodes. As a result, to parse each piece of information, one must specify
the unique hierarchy of nodes in which it is structured. This is known
as an XPath expression, and tells the parser how to navigate the XML
document to obtain the desired information. For example, the session
header date in Figure~\ref{fig-xml1} can be accessed using the XPath
expression ``\texttt{hansard/session.header/date}''. When specifying an
XPath expression, one can use an ``or'' operator to obtain elements from
multiple node paths at once, in the order that they appear in the
document. We did so throughout our script as we parsed uniquely nested
speech content, as it allows for the correct ordering of elements to be
maintained. We began our first script by parsing all the business start,
speech text, and Question Time contents contained in the XML document,
using these unique XPath expressions to do so. Hansard records contain a
number of statements throughout that were not explicitly spoken in
parliament. For example, the text in Figure~\ref{fig-content_ex} beneath
the bold subtitle ``Report from Federation Chamber'' is not attributed
to a particular member and was not spoken aloud during the parliamentary
proceedings. In contrast, the text which comes afterward was spoken
aloud in parliament by The Speaker at 14:01. Generally, unspoken text is
nested under \texttt{\textless{}debate.text\textgreater{}} or
\texttt{\textless{}subdebate.text\textgreater{}} nodes, while spoken
text is categorized under \texttt{\textless{}speech\textgreater{}}.
Importantly, in our work we focus primarily on parsing spoken speech
content (i.e.~what is nested within
\texttt{\textless{}speech\textgreater{}} nodes), such as what is stated
by The Speaker in Figure~\ref{fig-content_ex}. For this reason, many
Hansard transcriptions which are not spoken text may not be captured in
our database. In future work, capturing this unspoken content in our
database would be a priority.

The next step was to further develop our script to produce tidy data
sets containing all parsed text elements, where each statement is
separated onto its own row with details about the speaker, and rows are
maintained in chronological order. This first involved correcting the
variable classes and adding several indicator variables to differentiate
where statements came from, such as Chamber versus Federation Chamber or
sub-debate 1 versus sub-debate 2. The next key task stemmed from the
fact that the raw text data were not separated by each statement when
parsed. In other words, any interjections, comments made by The Speaker
or Deputy Speaker and continuations within an individual speech were all
parsed together as a single string. As such, the name, name ID,
electorate and party details were only provided for the person whose
turn it was to speak. Splitting up these speeches in a way which would
be generalizable across sitting days required much thought and effort.
Section~\ref{sec-interject} will provide further details on the
intricacies of this task.

Since we are looking at a wide time span of documents, there are many
changes in the way they are formatted over time. These became apparent
as we ran our script on XML files from earlier sitting days. Some
changes are as subtle as a differently named child-node, while others
are as extensive as a completely different nesting structure. Smaller
changes were accounted for as we became aware of them, and embedded into
the code in a way that would not cause issues for parsing more current
Hansards with subtle differences in formatting. However, as mentioned,
more significant changes in the XML structure of Hansard are what
necessitated the development of separate scripts as we worked backwards
in time. Further, while working backward in time, it became clear that
not every sitting day contains every possible XML element. For example,
some days did not have sub-debate 2 content, and some days did not have
a Federation Chamber proceeding. To improve the generalizability of
these scripts, if-else statements were embedded within the code wherever
an error might arise due to a missing element. For example, the entire
Federation Chamber block of code is wrapped in an if-else statement for
each script, so that it only executes if what the code attempts to parse
exists in the file.

Once the script ran without error for a few recent years of Hansard, we
continued to work backwards until extensive changes in tree structure
made our script incompatible with parsing earlier XML files. The
earliest sitting day our first script can successfully parse is 14
August 2012. Before developing new scripts to parse earlier Hansard
documents, we decided to prioritize cleaning and finalizing what we have
been able to parse. As such we continued building our script, fixing any
problems we noticed in the resulting datasets such as excess whitespace
or spacing issues, and splitting up any additional sections of the
parsed text onto separate rows where necessary. Specifically, we added a
section of our script to separate out general stage directions. More
information on this separation will be provided in
Section~\ref{sec-stage}. After completing our first script, it was
formatted as a function which takes a single file name argument and
produces one CSV file containing data on all proceedings from the given
sitting day.

@@

As previously mentioned, we developed a total of four scripts to parse
the 1998-2022 time frame of Hansard documents. Two main factors
motivated us to create four scripts as opposed to just one, the first
being structural variation in XML over time, and the second being
improved computational efficiency with separate scripts. While all four
scripts use the same general approach to parsing described in
Section~\ref{sec-overview} and produce the same CSV structure, the first
and second scripts use a different method of data processing than the
third and fourth scripts.

@@

While the modifications needed to develop the second script were quite
straightforward, this was not the case for our next script. The typical
tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
important difference from that of XMLs released after March 2011,
necessitating many changes to be made in our methodology. In XMLs after
March 2011, which our first two scripts successfully parse, the first
two child-nodes of \texttt{\textless{}speech\textgreater{}} are
typically \texttt{\textless{}talk.start\textgreater{}}, and
\texttt{\textless{}talk.text\textgreater{}}. The first child-node
contains data on the person whose turn it is to speak, and the second
contains the entire contents of that speech --- including all
interjections, comments, and continuations. After the
\texttt{\textless{}talk.text\textgreater{}} element closes, there are
typically a series of other child-nodes which provide a skeleton
structure for how the speech proceedings went in chronological order.
For example, if the speech began, was interrupted by one member, and
then continued uninterrupted until the end, there would be one
\texttt{\textless{}interjection\textgreater{}} node and one
\texttt{\textless{}continuation\textgreater{}} node following the
\texttt{\textless{}talk.text\textgreater{}} node. These would contain
details on the person who made each statement such as their party and
electorate.

@@

This was not isolated to just the beginning of speeches --- details on
individuals interjecting or commenting during speeches were also
captured this way. To separate statements out correctly, we collected
all of these patterns using the
\texttt{\textless{}talk.start\textgreater{}} node, and used them to
split statements wherever one of these patterns was found. After
separating the statements, we were able to remove these patterns from
the body of text. We also used this method of extracting and later
removing unwanted patterns for other pieces of data which did not belong
to the debate proceedings, such as sub-debate titles.

@@

Our approach to parse the \texttt{"chamber.xscript"} speeches used in
all four scripts meant that all questions without notice content was
already parsed in order. For the first two scripts, questions and
answers were already separated onto their own rows. For the third and
fourth scripts, just as we did with the rest of the speech content, we
used those patterns of data preceding the text to separate questions and
answers. Finally, since questions in writing exist in their own child
node we were able to use the same parsing method for all scripts, which
was simply to extract all question and answer elements from the
\texttt{"answers.to.questions"} child node.

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, questions were incorrectly transcribed under
an answer node and vice-versa, in which cases we manually corrected the
question and answer flags using the \texttt{str\_detect} function from
the \texttt{stringr} package. For instance, we check for any statements
flagged as questions which include the phrase ``has provided the
following answer to the honourable member's question'', in which case we
re-code that statement as an answer.

The next step was to merge Question Time contents with all the debate
speech. Doing so with the questions without notice content was
straightforward. As mentioned, our method of parsing meant that
everything was already parsed together in order, so we did not have to
perform any additional merging. For questions in writing, merging this
content was also straightforward due to the fact that it is always at
the very end of Hansard. This means that we could simply bind question
in writing rows to the bottom of the main dataframe. This approach was
used for all four scripts.

@@

Below is an example of part of a speech we would need to split,
extracted from Hansard on 30 November 2021, where Mr.~van Manen is
interrupted by The Speaker who states that the time for members'
statements has concluded.

@@

Next, we merged our main dataframe with the lookup table to replace any
incomplete names with their full names, and to fill in any gaps with
available name ID, electorate, party, gender, and unique ID information.
Finally, we were able to add a flag for interjections. Grouping our data
by the speech number, we defined an interjection as a statement made by
anyone who is not The Speaker, The Deputy Speaker, or the Member whose
turn it was to speak. Figure~\ref{fig-interject} provides an example of
a Federation Chamber proceeding with interjections. Evidently,
statements made by the original speaker Stuart Robert or by The Deputy
Speaker Maria Vamvakinou are not flagged as interjections.

@@

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{April 5, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many Commonwealth countries such as Canada,
the United Kingdom, and Australia (Vice and Farrell 2017). Given the
content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, the Hansard has been digitized for 1901 to 2019 (Beelen et
al. 2017). Having a digitized version of Hansard enables researchers to
conduct text analysis and statistical modelling. Following the lead of
that project, in this paper we introduce a similar database for
Australia. This is composed of individual datasets for each sitting day
in the House of Representatives from 1998 to 2022, containing details on
everything said in parliament in a form that can be readily used by
researchers. With the development of tools for large-scale text
analysis, this database will serve as a resource for understanding
political behaviour in Australia over time.

The Australian House of Representatives performs a number of crucial
governmental functions, such as creating new laws and overseeing
government expenditure (House of Representatives 2018, ch.~1). The House
operates under a parallel chamber setup, meaning there are two debate
venues where proceedings take place: the Chamber, and the Federation
Chamber. Sittings of the House follow a predefined order of business,
regulated by procedural rules called standing orders (House of
Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
number of scheduled proceedings including debates on government
business, 90 second member statements, and Question Time (House of
Representatives 2018, ch.~8). The Federation Chamber was created in 1994
as a subordinate debate venue of the Chamber. This allows for better
time management of House business as its proceedings occur
simultaneously with those of the Chamber (House of Representatives 2018,
ch.~21). Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members (House of Representatives 2018, ch.~21). It is the recording and
compilation of these proceedings on which Hansard is based, and it is
essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for
download from the official Parliament of Australia website in both PDF
and extensible markup language (XML) form. The PDF is the official
release. The PDF imposes formatting designed for humans to read with
ease, whereas XML is designed for consistency and machine legibility.
The nature of XML enables us to more easily use code to manipulate these
records at scale, motivating our choice to develop our database solely
using the XML formatted files. In cases where we were unsure on how to
proceed with processing the XML, we defer first to the PDF, and then to
the video recording of the proceeding, if available.

@@

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, Salisbury (2011) used online
Hansard records to investigate the occurrences of unparliamentary
comments by members of the House, where the Speaker tells that member to
withdraw their remark. Rasiah (2010) worked with Question Time data from
Hansard transcripts during February and March of 2003, to investigate
resistance of politicians in answering questions about Iraq. Fraussen,
Graham, and Halpin (2018) use Hansard to quantify political prominence
by investigating strategic mentions of interest groups by elected
officials. Finally, Alexander and Alexander (2021) construct a dataset
of the Australian Hansard, along with an analysis of the effect of
elections and changes in Prime Ministers upon topics mentioned in
parliament. Alexander and Alexander (2021) created this database with
the static PDF versions of Hansard, using OCR to digitize these files
into text which is suitable for analysis. This means there are
considerable digitization errors especially in the first half of the
dataset.

While there is evidently a growing body of literature on this topic,
there is still no comprehensive database for Australian Hansard based on
XML that spans from 1901 to the present day. Our work begins to bridge
this gap.

@@

Our database contains one comma-separated value (CSV) and one parquet
file for each sitting day of the House of Representatives from 02 March
1998 to 08 September 2022. We developed four scripts to produce these
files. Each script parses Hansard documents from a specific portion of
the 1998 to 2022 time frame.

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Finally, we discuss the script we developed to fill in remaining missing
details on the member of parliament speaking, which each file in our
database was passed to after being parsed and cleaned.

@@

The approach to parsing contents of an XML document depends on its tree
structure. As such, to create this database, we started by looking at a
single Hansard XML transcript from 2019. Doing so enabled us to identify
the various components of interest in the document, and how each one can
be parsed according to its corresponding structural form. Parsing was
performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
packages (Temple Lang 2022; Wickham, Hester, and Ooms 2021). Focusing on
one transcript also allowed us to ensure that all key components of the
transcript were parsed and captured in as much detail as possible. The
typical form of a Hansard XML transcript is summarized in the nested
list below. This provides an overview, but does not contain every
possible nested element that may be found in a Hansard XML.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child-nodes,
where the first child-node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. The Federation Chamber does not meet on every sitting
day, so this child element is not present in every XML file. The use of
separate child nodes allows for the distinction of proceedings between
the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with
\texttt{\textless{}business.start\textgreater{}} which is followed by a
series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child-node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child-node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the member of parliament whose turn it is to speak and
the time of their first statement. Unsurprisingly, speeches rarely go
uninterrupted in parliamentary debate settings --- they are often
composed of a series of interjections and continuations. These
statements are categorized under different sub-nodes depending on their
nature, such as \texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

Figure~\ref{fig-xml1} provides an example of the beginning of an XML
file for Hansard, which illustrates the structure outlined in the nested
list above. As stated, the XML structure begins with a parent element
\texttt{\textless{}hansard\textgreater{}} (highlighted in blue),
followed by a child element
\texttt{\textless{}session.header\textgreater{}} (highlighted in yellow)
with sub-child elements such as the date and parliament number, which
are all highlighted in pink. Next, there is the child element containing
everything that takes place in the Chamber,
\texttt{\textless{}chamber.xscript\textgreater{}}, which is also
highlighted in yellow in Figure~\ref{fig-xml1}. As previously mentioned,
the first sub-node of \texttt{\textless{}chamber.xscript\textgreater{}}
is \texttt{\textless{}business.start\textgreater{}}. The structure of
this can be seen between the nodes highlighted in green in
Figure~\ref{fig-xml1}, where the content we parse from the business
start is highlighted in orange.

@@

Evidently, the nature of XML formatting means that different pieces of
information are categorized under a series of uniquely named and nested
nodes. As a result, to parse each piece of information, one must specify
the unique hierarchy of the nodes in which it is structured. This is
known as an XPath expression, and tells the parser how to navigate the
XML document to obtain the desired information. For example, the session
header date in Figure~\ref{fig-xml1} can be accessed using the XPath
expression ``\texttt{hansard/session.header/date}''. When specifying an
XPath expression, one can use an ``or'' operator to obtain elements from
multiple node paths at once, in the order that they appear in the
document. We did so throughout our script as we parsed uniquely nested
speech content. This allows the correct ordering of elements to be
maintained. We began our first script by parsing all the business start,
speech text, and Question Time contents contained in the XML document,
using these unique XPath expressions to do so.

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by Wickham (2014). These contain all
parsed text elements, where each statement is separated onto its own row
with details about the member of parliament who is speaking, and rows
are maintained in chronological order. This first involved correcting
the variable classes and adding several indicator variables to
differentiate where statements came from, such as Chamber versus
Federation Chamber or \texttt{\textless{}subdebate.1\textgreater{}}
versus \texttt{\textless{}subdebate.2\textgreater{}}. The next key task
stemmed from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

Since we are looking at a wide time span of documents, there are many
changes in the way they are formatted. These became apparent as we ran
our script on XML files from earlier sitting days. Some changes are as
subtle as a differently named child-node, while others are as extensive
as a completely different nesting structure. Smaller changes were
accounted for as we became aware of them, and embedded into the code in
a way that would not cause issues for parsing more current Hansards with
subtle differences in formatting. However, as mentioned, more
significant changes in the XML structure of Hansard are what
necessitated the development of separate scripts as we worked backwards.
Further not every sitting day contains every possible XML element. For
example, some days did not have
\texttt{\textless{}subdebate.2\textgreater{}} content, and some days did
not have a Federation Chamber proceeding. To improve the
generalizability of these scripts, if-else statements were embedded
within the code wherever an error might arise due to a missing element.
For example, the entire Federation Chamber block of code is wrapped in
an if-else statement for each script, so that it only executes if what
the code attempts to parse exists in the file.

Once the script ran without error for a few recent years of Hansard, we
continued to work backwards until extensive changes in tree structure
made our script incompatible with parsing earlier XML files. The
earliest sitting day this first script can successfully parse is 14
August 2012. Before developing new scripts to parse earlier Hansard
documents, we prioritized cleaning and finalizing what we had been able
to parse. As such we continued building our script, fixing any problems
we noticed in the resulting datasets such as excess whitespace or
spacing issues, and splitting up any additional sections of the parsed
text onto separate rows where necessary. Specifically, we added a
section of our script to separate out general stage directions. More
information on this separation will be provided in
Section~\ref{sec-stage}. After completing our first script, it was
formatted as a function which takes a single file name argument and
produces one CSV file containing data on all proceedings from the given
sitting day.

@@

As mentioned, we developed a total of four scripts to parse the
1998-2022 time frame of Hansard documents. Two main factors motivated us
to create four scripts as opposed to just one, the first being
structural variation in XML over time, and the second being improved
computational efficiency with separate scripts. While all four scripts
use the same general approach to parsing described in
Section~\ref{sec-overview} and produce the same CSV structure, the first
and second scripts use a different method of data processing than the
third and fourth scripts.

@@

While the modifications needed to develop the second script were
straightforward, this was not the case for our next script. The typical
tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
important difference from that of XMLs released after March 2011,
necessitating many changes to be made in our methodology. In XMLs after
March 2011, which our first two scripts successfully parse, the first
two child-nodes of \texttt{\textless{}speech\textgreater{}} are
typically \texttt{\textless{}talk.start\textgreater{}}, and
\texttt{\textless{}talk.text\textgreater{}}. The first child-node
contains data on the person whose turn it is to speak, and the second
contains the entire contents of that speech --- including all
interjections, comments, and continuations. After the
\texttt{\textless{}talk.text\textgreater{}} element closes, there are
typically a series of other child-nodes which provide a skeleton
structure for how the speech proceedings went in chronological order.
For example, if the speech began, was interrupted by one member, and
then continued uninterrupted until the end, there would be one
\texttt{\textless{}interjection\textgreater{}} node and one
\texttt{\textless{}continuation\textgreater{}} node following the
\texttt{\textless{}talk.text\textgreater{}} node. These would contain
details on the person who made each statement, such as their party and
electorate.

@@

This was not isolated to just the beginning of speeches --- details on
individuals interjecting or commenting during speeches were also
captured this way. To separate statements correctly, we collected all of
these patterns using the \texttt{\textless{}talk.start\textgreater{}}
node, and used them to split statements wherever one of these patterns
was found. After separating the statements, we were able to remove these
patterns from the body of text. We also used this method of extracting
and later removing unwanted patterns for other pieces of data which did
not belong to the debate proceedings, such as sub-debate titles.

@@

Our approach to parse the \texttt{"chamber.xscript"} speeches used in
all four scripts meant that all questions without notice content was
already parsed in order. For the first two scripts, questions and
answers were already separated onto their own rows. For the third and
fourth scripts, just as we did with the rest of the speech content, we
used those patterns of data preceding the text to separate questions and
answers. Finally, since questions in writing exist in their own child
node we were able to use the same parsing method for all scripts, which
was to extract all question and answer elements from the
\texttt{"answers.to.questions"} child node.

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, questions were incorrectly transcribed under
an answer node and vice-versa, in which cases we manually corrected the
question and answer flags. For instance, we check for any statements
flagged as questions which include the phrase ``has provided the
following answer to the honourable member's question'', in which case we
re-code that statement as an answer.

The next step was to merge Question Time contents with all the debate
speech. Our method of parsing meant that everything was already in
order, so we did not have to perform any additional merging. For
questions in writing, merging this content was also straightforward due
to the fact that it is always at the end of Hansard. This means that we
could bind question in writing rows to the bottom of the main dataframe.
This approach was used for all four scripts.

@@

Below is an example of part of a speech we would need to split,
extracted from Hansard on 30 November 2021, where Bert van Manen is
interrupted by the Speaker who states that the time for members'
statements has concluded.

@@

Next, we merged our main dataframe with the lookup table to replace any
incomplete names with their full names, and to fill in any gaps with
available name ID, electorate, party, gender, and unique ID information.
Finally, we were able to add a flag for interjections. Grouping our data
by the speech number, we defined an interjection as a statement made by
anyone who is not the Speaker, the Deputy Speaker, or the member whose
turn it was to speak. Figure~\ref{fig-interject} provides an example of
a Federation Chamber proceeding with interjections. Statements made by
the member whose turn it was to speak, or by the Deputy Speaker Maria
Vamvakinou, are not flagged as interjections.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
Wickham, Hadley. 2014. {``Tidy Data.''} \emph{Journal of Statistical
Software} 59 (10). \url{https://doi.org/10.18637/jss.v059.i10}.
